Incentivizing Exploration with Unbiased Histories

### 2019-02-01 COLT 2019 Submission/3level.tex
figure =>appendix
Some more space-saving.
Added pageref's to references to figures.

\begin{construction}
The \emph{three-level policy} is defined as follows. The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}. Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration  (see Figure~\ref{fig:3level}).

The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $G$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $G$ are connected to the same nodes outside of $G$, but not to one another.}
\end{align}

@@

The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $G$ and second-level groups $G'$, whereby each agent in $G'$ observes the full history from the corresponding group $G$. More formally, agent in $G'$ is connected to the last node of each full-disclosure path in $G$. In other words, this agent receives message
    $\SubH{S}$,
where $S$ is the set of all rounds in $G$.
\end{construction}

\begin{figure}[t]
\centering
\begin{tikzpicture}
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw (\x+1,1)--(\x+1,2);
 \draw(\x+0.33,1)--(\x+1,2);
 \draw(\x+1.66,1)--(\x+1,2);
 %\draw(\x+1.4,1)--(\x+1,2);
 %\draw(\x+1.8,1)--(\x+1,2);
 \draw(\x+0.66,0)--(\x+0.66,1);
 \draw(\x+1.33,0)--(\x+1.33,1);
% \draw (\x+1.2,0)--(\x+1.2,1);
 %\draw(\x+1.6,0)--(\x+1.6,1);
 \node at(\x+1,2.5){$T_2$ rounds};
 \node at(\x+0.33, 0.5){$\GdT$};
 %\node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdots$};
 %\node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.66, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$};
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ paths};
 }
  \node at(5,4.5){all remaining rounds};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Level 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

@@

\end{tikzpicture}
\caption{Info-graph for the three-level policy. Each red box in level 1 corresponds to $T_1$ full-disclosure paths of length $\GdT$ each.}
\label{fig:3level}
\end{figure}

The key idea is as follows. Consider the gap parameter $\Delta = |\mu_1-\mu_2|$. If it is is large, then each first-level group produces enough data to determine the best arm with high confidence, and so each agent in the upper levels chooses the best arm. If $\Delta$ is small, then due to \emph{anti-concentration} each arm gets ``lucky" within  at least once first-level group, in the sense that it appears much better than the other arm based on the data collected in this group (and therefore this arm gets explored by the corresponding second-level group). To summarize, the middle level exploits if the gap parameter is large, and provides some more exploration if it is small.

@@

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of what the algorithm does. In the large gap case, the regret only comes from the
first level, so it is upper-bounded by the total number of agents in this level, which is
    $\NG\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$.
In both intermediate cases, it suffices to bound the regret from the
first and second levels, so
\[ \textstyle
\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2)
\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
= O(T^{4/7} \log^{6/7}(T)).
\]
Therefore, we obtain the stated regret bound in all cases.

>>>>

\begin{construction}
The \emph{three-level policy} is defined as follows (see Figure~\ref{fig:3level} on page \pageref{fig:3level}). The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}. Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration. The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $G$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $G$ are connected to the same nodes outside of $G$, but not to one another.}
\end{align}

@@

The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $G$ and second-level groups $G'$, whereby each agent in $G'$ observes the full history from the corresponding group $G$. More formally, agent in $G'$ is connected to the last node of each full-disclosure path in $G$. In other words, this agent receives message
    $\SubH{S}$,
where $S$ is the set of all rounds in $G$.
\end{construction}
\iffalse
\begin{figure}[t]
\centering
\begin{tikzpicture}
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw (\x+1,1)--(\x+1,2);
 \draw(\x+0.33,1)--(\x+1,2);
 \draw(\x+1.66,1)--(\x+1,2);
 %\draw(\x+1.4,1)--(\x+1,2);
 %\draw(\x+1.8,1)--(\x+1,2);
 \draw(\x+0.66,0)--(\x+0.66,1);
 \draw(\x+1.33,0)--(\x+1.33,1);
% \draw (\x+1.2,0)--(\x+1.2,1);
 %\draw(\x+1.6,0)--(\x+1.6,1);
 \node at(\x+1,2.5){$T_2$ rounds};
 \node at(\x+0.33, 0.5){$\GdT$};
 %\node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdots$};
 %\node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.66, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$};
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ paths};
 }
  \node at(5,4.5){all remaining rounds};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Level 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

@@

\end{tikzpicture}
\caption{Info-graph for the three-level policy. Each red box in level 1 corresponds to $T_1$ full-disclosure paths of length $\GdT$ each.}
\label{fig:3level}
\end{figure}
\fi
The key idea is as follows. Consider the gap parameter $\Delta = |\mu_1-\mu_2|$. If it is is large, then each first-level group produces enough data to determine the best arm with high confidence, and so each agent in the upper levels chooses the best arm. If $\Delta$ is small, then due to \emph{anti-concentration} each arm gets ``lucky" within  at least once first-level group, in the sense that it appears much better than the other arm based on the data collected in this group (and therefore this arm gets explored by the corresponding second-level group). To summarize, the middle level exploits if the gap parameter is large, and provides some more exploration if it is small.

@@

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of what the algorithm does. In the large gap case, the regret only comes from the
first level, so it is upper-bounded by the total number of agents in this level, which is
    $\NG\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$.
In both intermediate cases, it suffices to bound the regret from the
first and second levels, so
%\[ \textstyle
$\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2)
\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$,
which is at most 
$O(T^{4/7} \log^{6/7}(T))$.
%\]
Therefore, we obtain the stated regret bound in all cases.
